\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}

### 2023-02-26 R/Supp_Info_1.Rmd
add table to show the final data used to produce Figure 2

library(googlesheets4)
library(here)
library(readr)

@@

Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration.

@@

The data table features a first column listing the ways to use GitHub that were addressed in the manuscript (`r paste0(uses[1:13], collapse = "; " )`).

>>>>

library(googlesheets4)
library(here)
library(readr)
library(dplyr)

@@

@@

\newpage

```{r, echo = FALSE}
to_print = scatterblob_data[-6,-c(2,3,5,9:11)]
colnames(to_print) = c("GitHub Use Cases", 
                       "Cognitive Load",
                       "Technical Difficulty",
                       "Degree of Collaboration (Minimum)",
                       "Degree of Collaboration (Maximum)")
knitr::kable(to_print, 
             label = "data",
             caption = "Indices of technical difficulty and degree of collaboration for each GitHub use case. The first column lists the GitHub use cases that were addressed in the main text. Indices were assessed collaboratively following the steps in Appendix S1.1.",
              align = c('l','c','c','c','c')) %>% 
  kableExtra::column_spec(1, width = "3.5cm") %>%
  kableExtra::column_spec(2:5, width = "2cm")
```

\newpage
